>

### 2024-12-11 docs/article.qmd
Rearrange the results section to improve readability and reading flow

@@

IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction. @tbl-overview-patient depicts the dynamics of the population from 2018 to 2022. The ratio of male to female did not vary by a large margin, and the average age steadily increased over the year. These findings imply that the cohort stays relatively stable overtime without any indication of sudden demographic changes.

@@

The highest average of prescription claim occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] prescriptions. Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] prescriptions. A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in table [-@tbl-overview-daily] and figure [-@fig-period-day]. The cyclical patterns are further explained in our supplementary material. @tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.

@@

>>>>

## Description of the population

@@

IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction. @tbl-overview-patient captures the dynamics of the population from 2018 to 2022. The ratio of male to female only varied slightly, and the average age steadily increased over the year. These findings imply that the population demography stays relatively stable overtime without any indication of sudden changes.

@@

## Weekly variation of prescription dispensing

The highest average of prescription dispensing occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] prescriptions. Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] prescriptions. A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in @tbl-overview-daily. The cyclical patterns are further explained in our supplementary material. @tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.

@@

## Polypharmacy in the population

@tbl-res-poly outlines the type of polypharmacy in the population. The summary statistics were based on prescription-day data aggregated at the population level over the year. Prescription-day is the number of medications dispensed on a given day. For example, if seven medications are prescribed for one day, it accounts for 7 prescription-days. Same-class polypharmacy refers to co-prescription of psychopharmaca from the same class, such as a combination of antidepressants. Multi-class polypharmacy involves co-prescription of psychopharmaca from different classes, such as combining antidepressants and anxiolytics. Total polypharmacy refers to the overall number of co-prescriptions, including those involving medications outside psychopharmaca classes. Two statistics are reported in @tbl-res-poly: the sum and the mean with its standard deviation. The sum indicates the total prescription-days of polypharmacy within a year. The mean and standard deviation represent the average number of prescription-days per person for any polypharmacy regimen. Thus, we can read the findings as follow:

> *"In 2018, same-class polypharmacy of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person. For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which polypharmacy regimens occurred."*
